---
title: "Git Workshop"
subtitle: "Advanced stuff"
author: "Christoph Koch, Ondrej Zika, Lennart Wittkuhn"
institute: "Max Planck Research Group NeuroCode"
date: "Last update: `r format(Sys.time(), '%d %B, %Y')`"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts] 
    self_contained: true
    yolo: false
    lib_dir: libs
    nature:
      highlightStyle: solarized-dark
      highlightLines: true
      countIncrementalSlides: false
---

```{r, echo=FALSE}
library(xaringan)
# xaringan::inf_mr()
# http://jenrichmond.rbind.io/post/infinite-moon-reader/
```

```{css, echo=FALSE}
@media print {
  .has-continuation {
    display: block !important;
  }
}
```

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(knitr)
opts_chunk$set(
  fig.align="center", #fig.width=6, fig.height=4.5, 
  # out.width="748px", #out.length="520.75px",
  dpi = 300, #fig.path='Figs/',
  cache = T#, echo=F, warning=F, message=F
  )
```

# Table of contents

1. [Submodules](#submodules)

---

# Submodules

"I want to use code from function X" `git status`

### How does it work

- Submodules allow you to keep a Git repository as a subdirectory of another Git repository


### Advantages

- Avoiding redundancy
- Allowing reusability
- Independent commit history

---

### 

1. Adding an existing Git repository as a submodule

```bash
git submodule add https://github.com/chaconinc/DbConnector
```


---

# Git submodules: Adding a submodule

```bash
$ git submodule add https://git.mpib-berlin.mpg.de/neurocode/neurocode_tools.git
```

The `neurocode_tools` Git repo will be cloned into the `neurocode_tools` subdirectory:

```bash
Cloning into '/Users/wittkuhn/neurocode/git-workshop-examples/neurocode_tools'...
remote: Enumerating objects: 97, done.
remote: Counting objects: 100% (97/97), done.
remote: Compressing objects: 100% (62/62), done.
remote: Total 97 (delta 27), reused 70 (delta 21), pack-reused 0
Unpacking objects: 100% (97/97), done.
```

By default, submodules will add the subproject into a directory named the same as the repository, in this case “DbConnector”. You can add a different path at the end of the command if you want it to go elsewhere.

```bash
git submodule add https://git.mpib-berlin.mpg.de/neurocode/neurocode_tools.git \
awesome_tools
```

---

# Git Submodules: What happened?

Let's run `git status` to see what happened to our repo:

```bash
$ git status
On branch master
Your branch is up to date with 'origin/master'.

Changes to be committed:
  (use "git reset HEAD <file>..." to unstage)

	new file:   .gitmodules
	new file:   neurocode_tools
```

There are two new files:

1. `.gitmodules`
1. `neurocode_tools`

Let's check out what those files are!

---

## Git submodules: What is in `.gitmodules`?

`.gitmodules` stores the mapping between the submodule's URL and the local subdirectory you've pulled it into.

```bash
$ cat .gitmodules
[submodule "neurocode_tools"]
	path = neurocode_tools
	url = https://git.mpib-berlin.mpg.de/neurocode/neurocode_tools
```

- Multiple submodules will lead to multiple entries in `.gitmodules`
- Committing `.gitmodules` to your repo is important, so that collaborators know where to get the submodule from
- Make sure that the URL in `.gitmodules` is accessible by others
- To overwrite the URL use `git config submodule.<submodule_name>.url <new_url>`

---

## Git submodules: What is in `neurocode_tools`?

```{bash, eval=FALSE}
$ git diff --cached neurocode_tools
diff --git a/neurocode_tools b/neurocode_tools
new file mode 160000
index 0000000..383a616
--- /dev/null
+++ b/neurocode_tools
@@ -0,0 +1 @@
+Subproject commit 383a616af6d972313c6cf5e3ab743aecc5fed6cd
```

Cryptic!

Although `neurocode_tools` is a subdirectory in your repo, Git doesn't track its contents (when you are not in that directory) but sees it as as submodule.

Instead, Git references one particular commit of that repository: `Subproject commit 383a616af6d972313c6cf5e3ab743aecc5fed6cd`.

---

Let's add and commit the submodule (using combined add and commit with `-am`) ...

```{bash, eval=FALSE}
{{$ git commit -am "Add neurocode_tools module"}}
[master df9a330] Add neurocode_tools module
 2 files changed, 4 insertions(+)
 create mode 100644 .gitmodules
 create mode 160000 neurocode_tools
```

... and push! 🚀

```{bash, eval=FALSE}
{{$ git push origin master}}
Enumerating objects: 4, done.
Counting objects: 100% (4/4), done.
Delta compression using up to 4 threads
Compressing objects: 100% (3/3), done.
Writing objects: 100% (3/3), 426 bytes | 426.00 KiB/s, done.
Total 3 (delta 0), reused 0 (delta 0)
To git.mpib-berlin.mpg.de:neurocode/git-workshop-examples.git
   1fbe5b6..df9a330  master -> master
```

---

```{bash, eval=FALSE}
{{$ ls}}
README.md       neurocode_tools
```

Now we can `cd` into the `neurocode_tools` submodule and access its files:

```{bash, eval=FALSE}
{{$ cd neurocode_tools && ls}}
README.md  docs       javascript matlab     r
```

---

# Submodules (continued)

## Further reading

- https://git-scm.com/book/en/v2/Git-Tools-Submodules




