---
title: "Git Workshop"
subtitle: "Advanced stuff"
author: "Christoph Koch, Ondrej Zika, Lennart Wittkuhn"
institute: "Max Planck Research Group NeuroCode"
date: "Last update: `r format(Sys.time(), '%d %B, %Y')`"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts] 
    self_contained: true
    yolo: false
    lib_dir: libs
    nature:
      highlightStyle: solarized-dark
      highlightLines: true
      countIncrementalSlides: false
---

```{r, echo=FALSE}
library(xaringan)
# xaringan::inf_mr()
# http://jenrichmond.rbind.io/post/infinite-moon-reader/
```

```{css, echo=FALSE}
@media print {
  .has-continuation {
    display: block !important;
  }
}
```

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(knitr)
opts_chunk$set(
  fig.align="center", #fig.width=6, fig.height=4.5, 
  # out.width="748px", #out.length="520.75px",
  dpi = 300, #fig.path='Figs/',
  cache = T#, echo=F, warning=F, message=F
  )
```

# Table of contents

1. [Submodules](#submodules)

---

# Submodules

"I want to use code from function X" `git status`

### How does it work

- Submodules allow you to keep a Git repository as a subdirectory of another Git repository


### Advantages

- Avoiding redundancy
- Allowing reusability
- Independent commit history

---

### 

1. Adding an existing Git repository as a submodule

```bash
git submodule add https://github.com/chaconinc/DbConnector
```





---

# Submodules (continued)

## Further reading

- https://git-scm.com/book/en/v2/Git-Tools-Submodules




