---
title: "Git Workshop"
author: "Christoph Koch, Ondrej Zika, Lennart Wittkuhn"
affiliation: "Max Planck Research Group NeuroCode"
date: "Last update: `r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    toc: yes
    self_contained: true
    toc_float: true
    toc_depth: 3
    number_sections: false
    highlight: pygments
    theme: darkly
    code_folding: "hide"
    df_print: paged
    fig_caption: true
fig.align: "center"
---

# Overview

Welcome! 👋

- [Repo](https://git.mpib-berlin.mpg.de/neurocode/git-workshop/)
- [Post-workshop survey](https://forms.gle/UVSUKHs1hXLdXodC7) for feedback

```{r, echo=FALSE, message=FALSE}
# allow duplicate labels: https://bookdown.org/yihui/rmarkdown-cookbook/duplicate-label.html
options(knitr.duplicate.label = "allow")
```

```{r, echo=FALSE, message=FALSE}
if (!requireNamespace("pacman")) install.packages("pacman")
packages = c("here", "rmarkdown", "bookdown")
pacman::p_load(char = packages)
```

```{r, echo=FALSE, results="hide", message=FALSE, warning=FALSE}
path_images = here::here("content", "img")
path_public_images = here::here("public", "img")
```

```{r, echo=FALSE, results="hide", message=FALSE, warning=FALSE}
# copy input folder to public
system2(command = "mkdir", args = "public")
system2(command = "cp", args = sprintf("-r %s %s", path_images, path_public_images))
```

```{r, echo=FALSE, results="hide"}
render_xaringan = function(name, path_rmd){
  path_rmd_copy = here::here("public", paste0(name, ".Rmd"))
  system2(command = "cp", args = sprintf("%s %s", path_rmd, path_rmd_copy))
  name_html = paste0(name, ".html")
  path_html = here::here("public", name_html)
  rmarkdown::render(path_rmd_copy, 'all', output_file = path_html, output_dir = "public")
  return(name_html)
}
```

# Agenda

## 01 Introduction to Git

```{r, echo=FALSE, results="hide", message=FALSE, warning=FALSE}
path_html = render_xaringan(
  name = "01_introduction_to_git",
  path_rmd = here::here("content", "01_introduction_to_git.Rmd")
  )
```

- Presenter: Christoph Koch
```{r, echo=FALSE, results="asis"}
cat(paste0('- <a href="', path_html, '" target="_blank">Download slides</a>'))
```
- [Source code on GitLab](https://git.mpib-berlin.mpg.de/neurocode/git-workshop/-/blob/master/content/01_introduction_to_git.Rmd )

```{r, echo=FALSE}
knitr::include_url(path_html)
```

## 02a Collaboration using Git

```{r, echo=FALSE, results="hide", message=FALSE, warning=FALSE}
path_html = render_xaringan(
  name = "02_collaboration_using_git",
  path_rmd = here::here("content", "02_collaboration_using_git.Rmd")
  )
```

- Presenter: Ondrej Zika
```{r, echo=FALSE, results="asis"}
cat(paste0('- <a href="', path_html, '" target="_blank">Download slides</a>'))
```
- [Source code on GitLab](https://git.mpib-berlin.mpg.de/neurocode/git-workshop/-/blob/master/content/02_collaboration_using_git.Rmd)

```{r, echo=FALSE}
knitr::include_url(path_html)
```

## 02b Project Managament with Git

```{r, echo=FALSE, results="hide", message=FALSE, warning=FALSE}
path_html = render_xaringan(
  name = "02b_project_management.Rmd",
  path_rmd = here::here("content", "02b_project_management.Rmd")
  )
```

- Presenter: Christoph Koch
```{r, echo=FALSE, results="asis"}
cat(paste0('- <a href="', path_html, '" target="_blank">Download slides</a>'))
```
- [Source code on GitLab](https://git.mpib-berlin.mpg.de/neurocode/git-workshop/-/blob/master/content/02b_project_management.Rmd)

```{r, echo=FALSE}
knitr::include_url(path_html)
```

## 03 Git Submodules

```{r, echo=FALSE, results="hide", message=FALSE, warning=FALSE}
path_html = render_xaringan(
  name = "git-submodules",
  path_rmd = here::here("content", "git-submodules.Rmd")
  )
```

- Presenter: Lennart Wittkuhn
```{r, echo=FALSE, results="asis"}
cat(paste0('- <a href="', path_html, '" target="_blank">Download slides</a>'))
```
- [Source code on GitLab](https://git.mpib-berlin.mpg.de/neurocode/git-workshop/-/blob/master/content/git-submodules.Rmd)

```{r, echo=FALSE}
knitr::include_url(path_html)
```

## 04 Working with the wiki using Git

```{r, echo=FALSE, results="hide", message=FALSE, warning=FALSE}
path_html = render_xaringan(
  name = "git-wiki",
  path_rmd = here::here("content", "git-wiki.Rmd")
  )
```

- Presenter: Lennart Wittkuhn
```{r, echo=FALSE, results="asis"}
cat(paste0('- <a href="', path_html, '" target="_blank">Download slides</a>'))
```
- [Source code on GitLab](https://git.mpib-berlin.mpg.de/neurocode/git-workshop/-/blob/master/content/git-wiki.Rmd)

```{r, echo=FALSE}
knitr::include_url(path_html)
```
